Clause Size Reduction with \alluip Learning

### 2020-05-15 paper.tex
fix a typo

On the SAT 2019 race winner $\MapleNineShort$, all four
$\stablealluip$ configurations solved instances 2, 6, 5 and 5 more instances
than \oneuip, respectively. $\MapleNineShort$ prioritizes clauses that
are learned multiple times. We observed that
$\stablealluip$ clauses are less likely to be duplicated. As an
example, $\allUipMin$ in average, added 12\% less duplicated clauses
into the core clause database than \oneuip. This observation is
surprising, and the cause is unclear.

@@

$\defaultcadical$ with \oneuip solved 249 total instances. 
Applying $\allUipAct$ and $\allUipIn$ helped the solver solve 3 and 2 more instances, respectively.  
The average learnt clause size of \oneuip on 
$\defaultcadical$ is much larger than other solvers' (101 vs 60) 
while the average clause size of $\stablealluip$ configurations are similar on all solvers.

>>>>

On the SAT 2019 race winner $\MapleNineShort$, all four
$\stablealluip$ configurations solved 2, 6, 5 and 5 more instances
than \oneuip, respectively. $\MapleNineShort$ prioritizes clauses that
are learned multiple times. We observed that
$\stablealluip$ clauses are less likely to be duplicated. As an
example, $\allUipMin$ in average, added 12\% less duplicated clauses
into the core clause database than \oneuip. This observation is
surprising, and the cause is unclear.

@@

$\defaultcadical$ with \oneuip solved 249  instances. 
Applying $\allUipAct$ and $\allUipIn$ helped the solver solve 3 and 2 more instances, respectively.  
The average learnt clause size of \oneuip on 
$\defaultcadical$ is much larger than other solvers' (101 vs 60) 
while the average clause size of $\stablealluip$ configurations are similar on all solvers.
